---
format:
    html:
        output-ext: "html"
---

## Data Analysis Overview

* Table of Content
  + [Analysis Overview](DGE_Marker_Analysis.html)
    - [Chapter 1 Differential Gene Expression Calculations](DGE_chapter_1_DGE_calc_and_celltype_plots.htm)
    - [Chapter 2 DGE tables](DGE_chapter_2_tables.htm)
    - [Chapter 3 MA- and Volcanoplots](DGE_chapter_3_MA_and_violin_plots.htm)
    - [Chapter 4 Enrichment Analysis](DGE_chapter_4_enrichment_analysis.htm)


```{bash, eval=FALSE, echo=TRUE, results=FALSE, echo=FALSE}

ml Singularity/3.11.3
singularity shell --bind  /nemo:/nemo,/camp:/camp /nemo/stp/babs/working/boeings/singularity_images/r431.ubuntu.22.04.sif;
R
```

```{r setup, include=FALSE, echo =FALSE}

## This clearing  becomes necessary, in order to save the workspace between chapers. ##
rm(list = ls())

knitr::opts_chunk$set(
    tidy = F,
    tidy.opts = list(width.cutoff = 120),
    message = FALSE,
    warning = FALSE
)
```

```{r, eval=TRUE, echo=F, results=F}
# Footnote organiser based on: https://stackoverflow.com/questions/74632879/use-footnote-multiple-times-in-html-quarto
#| echo: false

gen_fn <- function(n, id) {
  # n is number of footnote
  # id is a unique id for that footnote
  paste0('<a href="#',id, '" class="footnote-ref" role="doc-noteref" aria-expanded="false"><sup>', n, '</sup></a>')
}

# Usage:
# Some example text for a footnote`r gen_fn(1, "fn1")`
# Some example text for same footnote`r gen_fn(1, "fn1")

```

```{r, eval=TRUE, echo=F, results=F}
###############################################################################
##                                                                           ##
if (!requireNamespace("remotes")){
  install.packages("remotes")
}


if (!requireNamespace("renv")){
  remotes::install_github("rstudio/renv")
}

if (!file.exists("renv.lock")){
    renv::init(
        biocondutor = TRUE
    )
} else {
    renv::restore(prompt = FALSE)
}

## Done                                                                      ##
###############################################################################


```


```{r, eval=FALSE, echo=F, results=F}
## Update to Seurat 5 / 4.9.9
renv::install("mojaveazure/seurat-object@seurat5")
renv::install("satijalab/seurat@seurat5")
packageVersion("Seurat")
```


<!-- Running Individual Modules in R -->
<!-- For example rmarkdown::render("src/modules/settings/partB.set.parameters.Rmd", output_dir = "..") -->

<!-- Essential 1: Set Analysis Parameters Chapter/Module (output required later) -->
```{r child = '_01-laod.data.and.set.parameters.qmd', eval=FALSE, echo=F}
```

<!-- Optional 2: Retrieve Reference Genes from Database or Gmt file -->
```{r child = '_02-load.or.define.gene.categories.qmd', eval=FALSE, echo=F}
```

Additional text regarding this particular analysis can be added here. For example:
2023-10-09: Addition of abc def.

<!-- Optional 6: (output required later): Create Integrated Seurat Object Chapter/Module -->
```{r child = '_06-add.documentation.qmd', eval=FALSE, echo=F}
```

```{r create_report_params, eval=T, results="asis", echo=F}
source("load.biologic.robj.R")

## Get report details
documentationParams <- list(

    "title" = "Pseudobulk Differential Gene Expression Analysis",
    "subtitle" =  "Test text for subtitle",
    "abstract" = "Test text for project abstract. ",
    "additionalParagraph" = "This is additional text for the abstract. "

)


## Try to retrieve project data from db ##
library(RMySQL)
db.pwd2 <- "_asf_"
db.user2 <- "asf"
host2 <- "ms1.thecrick.org"
projectParams <- documentationParams

tryCatch({
    dbDB = dbConnect(drv = RMySQL::MySQL(), user = db.user2, password = db.pwd2, host = host2, dbname = "asf");
dfProposal =  dbGetQuery(dbDB, paste0("SELECT * FROM asf_proposals WHERE project_name ='",Obio@parameterList$lims.id,"'"));
dbDisconnect(dbDB)
  }, error = function(x) {
    message("Project Database could not be reached or has no entry in Obio@parameterList$lims.id for this analysis.")

})

if (exists("dfProposal")){
  if (nrow(dfProposal) == 1){
      if (!is.na(dfProposal[1,"ProjectAlias"]) & dfProposal[1,"ProjectAlias"] != ""){
          projectParams[["title"]] = paste0(dfProposal[1,"ProjectAlias"], " - ", dfProposal[1,"project_name"])
      }

      if (!is.na(dfProposal[1,"project_user"]) & dfProposal[1,"project_user"] != ""){
          projectParams[["subtitle"]] = paste0(dfProposal[1,"user_lab"], " Lab - ", dfProposal[1,"project_user"])
          projectParams[["subtitle"]] <- gsub("^ Lab - ", "", projectParams[["subtitle"]])

      }

      if (!is.na(dfProposal[1,"proposal_text"]) & dfProposal[1,"proposal_text"] != ""){
          projectParams[["abstract"]] = dfProposal[1,"proposal_text"]

      }
  }
}


## Escape all special characters
projectParams <- lapply(
  projectParams, function(x)
  #gsub("([.|()\\^{}+$*?]|\\[|\\])", "\\\\\1", x)
  gsub("([.|()/\\^{}+$*?]|\\[|\\])", " ", x)
)

projectParams <- lapply(
  projectParams, function(x)
  #gsub("([.|()\\^{}+$*?]|\\[|\\])", "\\\\\1", x)
  gsub("\\\n", " ", x)
)


if (is.null(projectParams$additionalParagraph)){
    projectParams$additionalParagraph <- ""
}



# rojectParams$title <- "Title"
# projectParams$abstract <- "This is the QC section."
# rojectParams$subtitle <- "Abstract"

```

---
title: '`r projectParams$title`'
subtitle:  '`r projectParams$subtitle`'
author:
    - Stefan Boeing ^[The Francis Crick Institute Bioinformatics and Biostatistics Service, stefan.boeing@crick.ac.uk]
date: 'Compiled: `r format(Sys.Date(), "%B %d, %Y")`'
abstract: |
    | `r projectParams$abstract`
    |
    | `r projectParams$additionalParagraph`

---
